Knowledge-based Detection of Arabic Entity Graphs using Morphology and Graph Transformations

### 2011-10-18 trunk/tex/cicling.tex
added necessary code for comparing accuracy and recall of learning names

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu
\documentclass[11pt]{article}
\usepackage{ijcnlp2011}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
%\DeclareMathOperator*{\argmax}{arg\,max}
%\setlength\titlebox{6.5cm}    % Expanding the titlebox

\usepackage{arabtex}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{color}
\usepackage{rotate}
\usepackage{rotating}
\usepackage{amsthm}
\usepackage{booktabs}

@@

%\title{Instructions for NAACL HLT 2010 Proceedings\Thanks{This...}}
\title{Automatic Hadith Graphs using Arabic Morphological Analysis}

@@

\begin{abstract}
\end{list}
A hadith in Islamic literature is a narration from the 
prophet Mohammad related by multiple narrators.
Establishing the authenticity of a hadith is an important task
based on which Islamic scholars issue rules that affect the life
of people around the world. 
The literature lacks an automated and exhaustive mechanism of 
authentication checks. 
This is currently manual work prone to error and almost
impossible to complete in the life time of a scholar due to the
large literature available. 
In this paper, we present a tool that uses 
an Arabic morphological analyzer 
to successfully automate the
analysis of three books of hadith selected 
arbitrarily and abstract 
each book into a graph of narrators related to each other. 
\end{abstract}

\section{Introduction}

@@

The authenticity of a \noArRL{.hady_t} depends on 
the credibility of the narrators as reported in 
separate biography books. 
The study of \noArRL{.hady_t} authentication is 
currently manual and error prone due to the huge number
of existing traditions and tradition books. 
Hadithopedia~\cite{Hadithopaedia:08}
reports that the tradition and biography
books for one of the Islamic sects amounts to more than 
300 thousand lines of text. 
Al-Azami\shortcite{Al-Azami-91} cites more than eleven books
of digitized tradition books each of several volumes, and a dozen
other biography and secondary authentication books such
as a geographical dictionary of places in hadith.

@@

Current morphological analyzers such as 
Buckwalter~\shortcite{Buckwalter:02},
Beesley~\shortcite{Beesley:01},
SAMA~\cite{Kulick:10},
and ElixirFM~\cite{Otakar:07} 
take as input white space delimited tokens~\cite{Kulick:10},
consider them as words,
and enumerate all possible solutions. 
This approach has several problems. 
First, a white space delimited token may have 
more than one word, referred to as ``run-on'' 
words~\cite{Buckwalter:04}.
Second, the exhaustive enumeration may not be efficient and may
not be necessary or appropriate
in some applications as noted in~\cite{Maamouri:10}. 
%Other morphological analyzers such as 
%Amira~\cite{Diab:07,Benajiba:07},
%MAGEAD~\cite{Habash:05}, and MADA+TOKAN~\cite{Habash:09} 
%use machine learning and support vector machines (SVM) 
%to disambiguate the morphological analysis at the expense 
%of efficiency. 
%Xerox rules can be compiled into specialized finite state
%machine (FSM) based analyzers as described in~\cite{Beesley:03}.
%However, the efficiency of the resulting analyzer depends on the
%way the Xerox rules are written. 
%This requires deep knowledge and insight from the user
%in compilation techniques, context free grammars, 
%and morphological analysis.
%context free grammar rules that can be automatically compiled
%into efficient non-deterministic finite state Automata (NDFSA).

@@

{\bf Sarf.~~~}
Sarf~\footnote{Sarf (name modified for blind review) }
is 
an {\em application-specific efficient
morphological analyzer} based on
non-deterministic finite state Automata 
driven by an application-specific controller customized 
by the user. 
%Each machine in Sarf takes one letter at a time as input
%and represents a valid morphological analysis.
The application-specific controller prunes false positives
early in the run by making a decision at every input letter
to control the machines.
Sarf builds on and extends the lexicon of 
Buckwalter~\shortcite{Buckwalter:02} 
with proper and location names extracted from different online 
sources~\footnote{\href{http://alasmaa.net/}{http://alasmaa.net/ }, 
\href{http://ar.wikipedia.org/}{http://ar.wikipedia.org/}}
as well as biblical sources~\footnote{Genesis 4:17-23; 5:1-32; 9:28-10:32; 11:10-32; 25:1-4, 12-18; 36:1-37:2; Exodus 6:14-25; Ruth 4:18-22; 1 Samuel 14:49-51; 1 Chronicles 1:1-9:44; 14:3-7; 24:1; 25:1-27:22; Nehemiah 12:8-26; Matthew 1:1-16; Luke 3:23-38}.

@@

%Sarf builds upon the lexicon of Buckwalter\shortcite{Buckwalter:02}.

@@

%Similar to Sarf, Beesley~\shortcite{Beesley:01} uses

@@

%{\bf Citations}: Citations within the text appear
%in parentheses as~\cite{Gusfield:97} or, if the author's name appears in
%the text itself, as Gusfield~\shortcite{Gusfield:97}. 
%Append lowercase letters to the year in cases of ambiguities.  
%Treat double authors as in~\cite{Aho:72}, but write as 
%in~\cite{Chandra:81} when more than two authors are involved. 
%Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}.

@@

%\bibliographystyle{naaclhlt2010}
\bibliographystyle{acl}
{\small \bibliography{fzAr}}
\nocite{completeBibleGenealogy:Online}
\end{document}

>>>>

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu
\documentclass{llncs}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
%\DeclareMathOperator*{\argmax}{arg\,max}
%\setlength\titlebox{6.5cm}    % Expanding the titlebox

\usepackage{arabtex}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{color}
\usepackage{rotate}
\usepackage{rotating}
%\usepackage{amsthm}
\usepackage{booktabs}

@@

%\title{Instructions for NAACL HLT 2010 Proceedings\Thanks{This...}}
\title{Knowledge-based Detection of Arabic Entity Graphs using Morphology and Graph Transformations}

@@

\begin{abstract}
A hadith in Islamic literature is a narration from the 
prophet Mohammad related by multiple narrators.
Establishing the authenticity of a hadith is an important task
based on which Islamic scholars issue rules that affect the life
of people around the world. 
The literature lacks an automated and exhaustive mechanism of 
authentication checks. 
This is currently manual work prone to error and almost
impossible to complete in the life time of a scholar due to the
large literature available. 
In this paper, we present a tool that uses 
an Arabic morphological analyzer 
to successfully automate the
analysis of three books of hadith selected 
arbitrarily and abstract 
each book into a graph of narrators related to each other. 
\end{abstract}

\section{Introduction}
 Arabic morphological rich
 entity detection in Arabic
 entity graphs
 locality of entities enables detection of entities and aggregating local clusters of entities into general graphs
 applications
 	bible genealogy 
 	hadith
 	bibliography
	travel itineraries
	others...
 learning and enriching gazetteers

\section{The Method}

Our method takes a set of documents and builds 
a graph where entities are nodes and edges are relations between the nodes. 
Our target graph has a predefined set of relations expressed as edge labels such as ``child'' and ``spouse''.
We use morphological analysis with finite-state machines to detect local entities and
relations between them.
We then use graph merging and comparison techniques to build the final general graphs.

In the sequel, we automatically learn entities and append them to our lexicon as new tags. 
We automatically learn lexicon items and infer their semantical meanings as relations in the 
graph merging phase. We express the inferred semantic meaning as a sequence of graph transformations
that removes the edge with the lexicon item and replaces it with edges with equivalent predefined labels.
We also interactively learn the semantics of other lexicon items that we detect as relations but could not infer their meaning 
in terms of the predefined set of relations.
The entities and relations are detected

Our method has two folds. At the first level, we detect entities and edges that
Given a lexicon that can distinguish entities and connections between them, and several documents that contain these entities,
we hypothesize that entities that occur next to each other are relevant entities even if their connections do not belong to the
connection lexicon. We also hypothesize that entities occur after connection are relevant entities.

-importance of cluster (Min number of entities in context)
-importance of tolerance 
-entities using lexicons
-clusters
-

\section{Application to Hadith}

@@

The authenticity of a \noArRL{.hady_t} depends on 
the credibility of the narrators as reported in 
separate biography books. 
The study of \noArRL{.hady_t} authentication is 
currently manual and error prone due to the huge number
of existing traditions and tradition books. 
Hadithopedia~\cite{Hadithopaedia:08}
reports that the tradition and biography
books for one of the Islamic sects amounts to more than 
300 thousand lines of text. 
Al-Azami\cite{Al-Azami-91} cites more than eleven books
of digitized tradition books each of several volumes, and a dozen
other biography and secondary authentication books such
as a geographical dictionary of places in hadith.

@@

Current morphological analyzers such as 
Buckwalter~\cite{Buckwalter:02},
Beesley~\cite{Beesley:01},
SAMA~\cite{Kulick:10},
and ElixirFM~\cite{Otakar:07} 
take as input white space delimited tokens~\cite{Kulick:10},
consider them as words,
and enumerate all possible solutions. 
This approach has several problems. 
First, a white space delimited token may have 
more than one word, referred to as ``run-on'' 
words~\cite{Buckwalter:04}.
Second, the exhaustive enumeration may not be efficient and may
not be necessary or appropriate
in some applications as noted in~\cite{Maamouri:10}. 
%Other morphological analyzers such as 
%Amira~\cite{Diab:07,Benajiba:07},
%MAGEAD~\cite{Habash:05}, and MADA+TOKAN~\cite{Habash:09} 
%use machine learning and support vector machines (SVM) 
%to disambiguate the morphological analysis at the expense 
%of efficiency. 
%Xerox rules can be compiled into specialized finite state
%machine (FSM) based analyzers as described in~\cite{Beesley:03}.
%However, the efficiency of the resulting analyzer depends on the
%way the Xerox rules are written. 
%This requires deep knowledge and insight from the user
%in compilation techniques, context free grammars, 
%and morphological analysis.
%context free grammar rules that can be automatically compiled
%into efficient non-deterministic finite state Automata (NDFSA).

@@

{\bf Sarf.~~~}
Sarf~\footnote{Sarf (name modified for blind review) }
is 
an {\em application-specific efficient
morphological analyzer} based on
non-deterministic finite state Automata 
driven by an application-specific controller customized 
by the user. 
%Each machine in Sarf takes one letter at a time as input
%and represents a valid morphological analysis.
The application-specific controller prunes false positives
early in the run by making a decision at every input letter
to control the machines.
Sarf builds on and extends the lexicon of 
Buckwalter~\cite{Buckwalter:02} 
with proper and location names extracted from different online 
sources~\footnote{\href{http://alasmaa.net/}{http://alasmaa.net/ }, 
\href{http://ar.wikipedia.org/}{http://ar.wikipedia.org/}}
as well as biblical sources~\footnote{Genesis 4:17-23; 5:1-32; 9:28-10:32; 11:10-32; 25:1-4, 12-18; 36:1-37:2; Exodus 6:14-25; Ruth 4:18-22; 1 Samuel 14:49-51; 1 Chronicles 1:1-9:44; 14:3-7; 24:1; 25:1-27:22; Nehemiah 12:8-26; Matthew 1:1-16; Luke 3:23-38}.

@@

%Sarf builds upon the lexicon of Buckwalter\cite{Buckwalter:02}.

@@

%Similar to Sarf, Beesley~\cite{Beesley:01} uses

@@

%{\bf Citations}: Citations within the text appear
%in parentheses as~\cite{Gusfield:97} or, if the author's name appears in
%the text itself, as Gusfield~\cite{Gusfield:97}. 
%Append lowercase letters to the year in cases of ambiguities.  
%Treat double authors as in~\cite{Aho:72}, but write as 
%in~\cite{Chandra:81} when more than two authors are involved. 
%Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}.

@@

%\bibliographystyle{naaclhlt2010}
\bibliographystyle{splncs03}

{\small \bibliography{fzAr}}

\nocite{completeBibleGenealogy:Online}

\end{document}
